Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-28 paper/paper.Rmd
clarified projection issues, dependency on upstream packages

Within the \pkg{mlr3} ecosystem, partitioning strategies are represented by their own objects of class \texttt{Resampling}, most of which are available within \pkg{mlr3} itself (e.g., regular random CV); other specialized strategies (e.g., \texttt{TaskClassifST} or \texttt{TaskRegrST}) are defined in extension packages such as \pkg{mlr3spatiotempcv}.
In the machine-learning pipeline, these objects define the data splits used for model evaluation and selection (hyperparameter tuning) by machine-learning algorithms.
<!--- They play an important role for an unbiased application of ML algorithms [@schratz2019]. [FIXME: Point gas been made before, it is unrelated to this section's topic.] -->

Resampling objects in \pkg{mlr3spatiotmpcv} inherit from class \texttt{mlr3::Resampling} and can be created from established object classes for geospatial data in R, including simple features [@pebesma2018], which facilitates their integration into domain-specific workflows in the geospatial sciences.
This includes support for geographic coordinate reference systems (CRS) and their respective distance measures in projected planar space or using great circle distances on the unprojected ellipsoid.
Non-spatial data tables with coordinates as variables are also supported.
If no projection is specified, World Geodetic System 1984 (WGS84, EPSG: 4326) is assumed. <!--- FIXME: Is this correct even for distance metrics? Wouldn't it be more natural to simply use Euclidean distance when no projection is specified? In many cases coordinates will be UTM, not lat/lon... Just wondering. -->

>>>>

Within the \pkg{mlr3} ecosystem, partitioning strategies are represented by their own objects of class \texttt{Resampling}, most of which are available within \pkg{mlr3} itself (e.g., regular random CV); other specialized strategies (e.g., \texttt{TaskClassifST} or \texttt{TaskRegrST}) are defined in extension packages such as \pkg{mlr3spatiotempcv}.
In the machine-learning pipeline, these objects define the data splits used for model evaluation and selection (hyperparameter tuning) by machine-learning algorithms. 
Spatial and spatiotemporal partitioning techniques in \pkg{mlr3spatiotempcv} are currently mostly imported and interfaced from other packages, in particular \pkg{sperrorest}, \pkg{blockCV}, \pkg{CAST} [@blockCV; @brenning2012; @CAST], in order to expose them to \pkg{mlr3} functionality.

Resampling objects in \pkg{mlr3spatiotmpcv} inherit from class \texttt{mlr3::Resampling} and can be created from established object classes for geospatial data in R, including simple features [@pebesma2018], which facilitates their integration into domain-specific workflows in the geospatial sciences.
Support for projected (planar) and unprojected (geographic) coordinate reference systems (CRS) currently varies depending on the partitioning techniques used, since these inherit their behaviour from the underlying R package.
It is planned to provide a more consistent interface that supports all CRS and allows the use of distance measures in projected planar space or using great circle distances on the unprojected ellipsoid, in the case of unprojected CRS.
Non-spatial data tables with coordinates as variables are also supported.
